Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-29 papers/ms.tex
update ms: spectra description

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 August 16 and 2021 October 25.  The acquisition
and analysis followed the standard reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  We derived the
stellar spectral parameters ($T_{\rm eff}, \log g, R_\star$) using
\texttt{SpecMatch-Emp} \citep{yee_SM_2017}, which yielded values in
$<1$-$\sigma$ agreement with those from the cluster-isochrone
approach.  This approach also yielded $[Fe/H]=0.13 \pm 0.09$.  Using
the broadened synthetic templates from \texttt{SpecMatch-Synth}
\citep{petigura_cksi_2017}, we found $v\sin i = 9.3 \pm 1.0\,\mkms$.
The systemic radial velocity at the two sequence epochs was $-9.1 \pm
1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$ respectively.  To infer the
equivalent width of the Li\,\textsc{I} 6708\,\AA\ doublet, we followed
the procedure described by \citet{bouma_2021_ngc2516}.  This yielded a
strong detection: ${\rm EW}_{\rm Li} = 126^{+8}_{-4}$\,m\AA, with
values consistent at $<1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the Fe\,\textsc{I} blend at
6707.44\AA.

@@

\paragraph{High-Resolution Imaging}
%FIXME TODO LEFT OFF HERE -- DESCRIBE!

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired TRES spectra on 2015 June 1.  The stellar
parameter classification pipeline for these spectra is described by
\citet{2021tsc2.confE.124B}, and is based on the template library
originally constructed by \citet{buchhave_hatp16b_class_2010}.

%FIXME TODO LEFT OFF HERE -- DESCRIBE!
vsini?  Fe/H?  Li EW?

@@

@@

KOI-7913 (YYYY/MM/DD and YYYY/MM/DD), where for the latter the two
different epochs corresponded to observations of the secondary and
primary respectively.

\paragraph{High-Resolution Imaging}
Is a binary.
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO

>>>>

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 August 16 and 2021 October 25.  The acquisition
and analysis followed the standard reduction techniques of the
California Planet Survey \citep{howard_cps_2010}.  We derived the
stellar parameters ($T_{\rm eff}, \log g, R_\star$) using
\texttt{SpecMatch-Emp} \citep{yee_SM_2017}, which yielded values in
$<1$-$\sigma$ agreement with those from the cluster-isochrone
approach.  This approach also yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using
the broadened synthetic templates from \texttt{SpecMatch-Synth}
\citep{petigura_cksi_2017}, we found $v\sin i = 9.3 \pm 1.0\,\mkms$.
The systemic radial velocity at the two sequence epochs was $-9.1 \pm
1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$ respectively.  To infer the
equivalent width of the Li\,\textsc{I} 6708\,\AA\ doublet, we followed
the procedure described by \citet{bouma_2021_ngc2516}.  This yielded a
strong detection: ${\rm EW}_{\rm Li} = 126^{+8}_{-4}$\,m\AA, with
values consistent at $<1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the Fe\,\textsc{I} blend at
6707.44\AA.

@@

\paragraph{High-Resolution Imaging}
{\bf todo}

\subsection{KOI-7368}
\paragraph{Spectra}
For KOI-7368, we acquired a spectrum using the echelle spectrograph
(TRES; \citealt{furesz_tres_2008}) mounted at the Tillinghast 1.5m at
the Fred Lawrence Whipple Observatory on Mt. Hopkins, AZ.  The
spectrum was acquired on 2015 June 1.  The stellar parameter
classification pipeline for these spectra is described by
\citet{2021tsc2.confE.124B}.  It is based on the synthetic template
library originally constructed by \citet{buchhave_hatp16b_class_2010}.
The resulting stellar parameters ($T_{\rm eff}, \log g, R_\star$)
agreed with those from the cluster-isochrone method within
$1$-$\sigma$, though the effective temperature is more precise by a
factor of three.  Auxiliary parameters included the metallicity $[{\rm
Fe/H}]= -0.02 \pm 0.08$, the equatorial velocity $v\sin i = 20.21 \pm
0.50\,\mkms$, and the systemic velocity ${\rm RV}_{\rm sys} = -10.9
\pm 0.2\,\mkms$.  The Li 6708\AA\ EW measurement procedure yielded
${\rm EW}_{\rm Li} = 236^{+16}_{-14}$\,m\AA.

@@

\paragraph{Binarity}

%(e.g., Jenkins KSCI-19081-002 KPDH pp 129, or many other pages)
KOI-7913 appears to be a binary.  The north-west
primary\footnote{Relevant identifiers for the primary are KIC 8873450
= Gaia DR2/EDR3 2106235301785454208.  For the secondary, they are KIC
8873448 = Gaia DR2/EDR3 2106235301785453824.  } is approximately 0.5
magnitudes brighter than the south-east secondary in optical passbands.
The two stars are separated in Gaia EDR3 by $3\farcs54$ on-sky, and
have parallaxes consistent within $1$-$\sigma$ (the average is
$\varpi=3.66 \pm 0.01$\,mas).  This corresponds to an apparent on-sky
separation of $959 \pm 2$ au.  Gaia EDR3 quotes
$(\mu_{\alpha'},\mu_\delta)=(2.439\pm0.015, 1.009\pm 0.016)\,{\rm
mas}\,{\rm yr}^{-1}$ for the primary, and
$(\mu_{\alpha'},\mu_\delta)=(2.696\pm0.020, 0.650 \pm 0.021) \,{\rm
mas}\,{\rm yr}^{-1}$ for the secondary.  Since two stars were resolved
in the Kepler Input Catalog and are roughly one Kepler pixel apart, an
accurate crowding metric has already been applied in the NASA Ames
data products to correct the mean flux level
\citep{2017ksci.rept....6M}.  This is important for deriving accurate
transit depths.

@@

We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The usual
\texttt{SpecMatch-Emp} \citep{yee_SM_2017} machinery yielded $T_{\rm
eff,A} = 4324 \pm 70\,{\rm K}$, $T_{\rm eff,B} = 4038 \pm 70\,{\rm
K}$.  The remaining parameters were in agreement with those from the
cluster isochrone.  For the primary, we also found $[{\rm Fe/H}]=
-0.06 \pm 0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm
sys} = -17.8 \pm 1.1\,\mkms$.  These same parameters for the secondary
were $[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$,
and ${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, 
lithium 6708\,\AA\ absorption is not expected for the
secondary, but might be present for the primary 
\citep[{\it e.g.},][Figure~8]{soderblom_ages_2014}.
Conversely,  {\bf todo finish}
% TODO: make this figure?

% For Li:
%    ~~~(CITE Figure 10 of Barrado y Navasceus 2004?).
%   ****USE FIG8 OF SODERBLOM+13****
% 
%   OR USE BAFFLES AS YOUR REFERENCE?
%     B-V=1.48 (primary), IC2602 age has no data.  beta pic age has lots of scatter
%     around this color, between 10mA and 100mA.
%     B-V=redder... 1.8?  SpType ~M0V, really no Li expected.
%   A: no... they really didn't collect very good data from what i see.
%   especially at the red end...
% 
% NW component SpType~K5.5-K6V; HIRES spectrum shows weak Li (EW 65 +/-
% 8 mA), Halpha in emission (double-peaked?!), and CaHK in emission.
% Reamatch SB2 checks don't show evidence for it being SB2.
% SW component SpType~K9V-M0V; HIRES spectrum shows H-alpha in emission
% (consistent with <150 Myr) and no Li (expected given Teff).
% Given the kinematics, the spectra paint a picture consistent with KOI
% 7913 being part of the ~40 Myr Cep-Her group.
